---
title: "Cakes and bricks: same shape, different impact"
author: Jean-Bob Delatourte
format:
  pdf:
    number-sections: true
    number-depth: 4
    keep-tex: true
    colorlinks: false
date: today
execute:
  echo: false
bibliography:
  papers: phd_papers.bib
  other: others.bib
  references: refs_list.bib
csl: apa-old-doi-prefix.csl
filters:
  - multibib
  - bold-author
bold-auth-name:
  - family: Delatarte
    given: J.-B.
validate-yaml: false
citeproc: false
crossref:
  custom:
    - kind: float
      key: apptbl
      latex-env: apptbl
      reference-prefix: Table A
      space-before-numbering: false
      latex-list-of-description: Appendix Table
nocite: |
  @stupid
  @coolpaper
  @thatotherpaper
---

```{r}
#| label: setup
#| include: false

knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
options(knitr.kable.NA = '')
options(tidyverse.quiet = TRUE)

```

# Scientific environment

# Acknowledgements

# Abstract in English

# Abstract in Norwegian

# List of Publications

## Publications included in the thesis

::: {#refs-papers}
:::

## Contributions to other publications during the PhD period

::: {#refs-other}
:::

## Authors contribution
```{r}
#| label: contributions
#| include: false

library(googlesheets4)
library(plume)
library(tidyverse)
library(rticles)
library(knitr)



paper1_authors <- read_sheet(gs4_find("authors_paper1"))

aut_paper1 <- Plume$new(paper1_authors)
contributions_paper1 <- aut_paper1$get_contributions(
  dotted_initials = FALSE,
  sep_last = ", "
) |>
c()

paper2_authors <- read_sheet(gs4_find("authors_paper2"))

aut_paper2 <- Plume$new(paper2_authors)
contributions_paper2 <- aut_paper2$get_contributions(
  dotted_initials = FALSE,
  sep_last = ", "
) |>
c()

grazingflux_authors <- read_sheet(gs4_find("authors_grazingcflux"))

aut_grazingflux <- Plume$new(grazingflux_authors)
contributions_grazingflux <- aut_grazingflux$get_contributions(
  dotted_initials = FALSE,
  sep_last = ", "
) |>
c()

inclineflux_authors <- read_sheet(gs4_find("authors_inclineflux"))

aut_inclineflux <- Plume$new(inclineflux_authors)
contributions_inclineflux <- aut_inclineflux$get_contributions(
  dotted_initials = FALSE,
  sep_last = ", "
) |>
c()

contrib_paper <- function(
  aut_vec, # a vector of author contributions as produced with aut$get_contributions() |> c()
  paper_name, # name of the paper
  split = ": " # same as divider in get_contributions
){
lapply(aut_vec, string_to_table, n = 2, split_regex = split) |>
  bind_rows() |>
  rename(
    Role = "X1",
    {{paper_name}} := "X2"
  )
}

contrib_paper1 <- contrib_paper(
  contributions_paper1,
  "Paper I"
)

contrib_paper2 <- contrib_paper(
  contributions_paper2,
  "Paper II"
)

contrib_tbl <- full_join(
  contrib_paper1,
  contrib_paper2,
  by = "Role"
)
```

```{r}
#| results: asis
#| tbl-colwidths: [30, 30, 30]
kable(contrib_tbl)
```

```{r}
#| label: authors
#| include: false

authors <- bind_rows(paper1_authors, paper2_authors) |>
  select(given_name, family_name, affiliation_1, affiliation_2) |>
  unique() |>
  mutate( # we add ranking to sort by me, supervisors, others
    ranking = 1
  ) |>
  arrange(ranking, family_name)

aut <- Plume$new(authors)

```

`r aut$get_author_list("^a^")`

```{r}
#| results: asis
aut$get_affiliations() |> cat(sep = "\n\n")
```


<!-- # Contents -->
\tableofcontents

# Introduction

# Aims of this thesis

We write smart things and we cite stuff @corriher2008bakewise.

# Methodological approach

# Results

# Discussion and remarks

# References

::: {#refs-references}
:::

# Paper I

# Paper II

# Paper III

# Paper IV