---
title: "Cakes and bricks: same shape, different impact"
author: Jean-Bob Delatourte
format:
  pdf:
    number-sections: true
    number-depth: 4
    colorlinks: false
    include-in-header: 
      text: |
        \usepackage{lipsum}
date: today
execute:
  echo: false
bibliography: refs_list.bib
csl: apa-old-doi-prefix.csl
nocite: |
  @stupid
  @coolpaper
  @thatotherpaper
---

\pagenumbering{Roman}

```{r}
#| label: setup
#| include: false

knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
options(knitr.kable.NA = '')
options(tidyverse.quiet = TRUE)

```

# List of Publications

{{< include paper_list.md >}}

## Authors contribution
```{r}
#| label: contributions
#| include: false

library(googlesheets4)
library(plume)
library(tidyverse)
library(rticles)
library(knitr)



paper1_authors <- read_sheet(gs4_find("authors_paper1"))

aut_paper1 <- Plume$new(paper1_authors)
contributions_paper1 <- aut_paper1$get_contributions(
  dotted_initials = FALSE,
  sep_last = ", "
) |>
c()

paper2_authors <- read_sheet(gs4_find("authors_paper2"))

aut_paper2 <- Plume$new(paper2_authors)
contributions_paper2 <- aut_paper2$get_contributions(
  dotted_initials = FALSE,
  sep_last = ", "
) |>
c()

contrib_paper <- function(
  aut_vec, # a vector of author contributions as produced with aut$get_contributions() |> c()
  paper_name, # name of the paper
  split = ": " # same as divider in get_contributions
){
lapply(aut_vec, string_to_table, n = 2, split_regex = split) |>
  bind_rows() |>
  rename(
    Role = "X1",
    {{paper_name}} := "X2"
  )
}

contrib_paper1 <- contrib_paper(
  contributions_paper1,
  "Paper I"
)

contrib_paper2 <- contrib_paper(
  contributions_paper2,
  "Paper II"
)

contrib_tbl <- full_join(
  contrib_paper1,
  contrib_paper2,
  by = "Role"
)
```

```{r}
#| results: asis
#| tbl-colwidths: [30, 30, 30]
kable(contrib_tbl)
```

```{r}
#| label: authors
#| include: false

authors <- bind_rows(paper1_authors, paper2_authors) |>
  select(given_name, family_name, affiliation_1, affiliation_2) |>
  unique() |>
  # pass this as comments first to see what the order is, and then attribute ranking and arrange
  mutate( # we add ranking to sort by me, supervisors, others
    ranking = c(1, 2, 3, 3)
  ) |>
  arrange(ranking, family_name)

aut <- Plume$new(authors)

```

`r aut$get_author_list("^a^")`

```{r}
#| results: asis
aut$get_affiliations() |> cat(sep = "\n\n")
```


<!-- # Contents -->
\tableofcontents
\newpage
\setcounter{section}{0}
\setcounter{page}{0}
\pagenumbering{arabic}

# Introduction

This is an introduction.

# Aims of this thesis

We write smart things and we cite stuff [@corriher2008bakewise].

Inline @lee2012literature blablabla.

Or just the year -@barham2001science and nothing else.

We can also cite a paper where we are co author [@delatourte2025] and the name will not be in bold in the references list.

## Sub section


\lipsum


# References {.unnumbered}

::: {#refs}
:::
