---
title: "Cakes and bricks: same shape, different impact"
author: Jean-Bob Delatourte
format:
  pdf:
    number-sections: false
    colorlinks: false
    include-in-header: 
      text: |
        \usepackage{lipsum}
  docx: default
date: today
execute:
  echo: false
bibliography: refs_list.bib
csl: apa-old-doi-prefix.csl
nocite: |
  @stupid
  @coolpaper
  @thatotherpaper
---

\pagenumbering{Roman}

```{r}
#| label: setup
#| include: false

knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
options(knitr.kable.NA = '')
options(tidyverse.quiet = TRUE)

my_packages <- c(
  "tibble",
    "googlesheets4",
    "plume",
    "tidyverse",
    "rticles",
    "knitr",
    "targets"
)

lapply(my_packages, library, character.only = TRUE)

```

# List of Publications


{{< include paper_list.md >}}

## Authors contribution
```{r}
#| label: contributions
#| include: false

authors_tbl <- tar_read(contrib_tbl)
authors <- tar_read(all_authors)

```

```{r}
#| results: asis
#| tbl-colwidths: [30, 30, 30]

kable(authors_tbl)
```

```{r}
#| label: authors
#| include: false



aut <- Plume$new(authors)

```

`r aut$get_author_list("^a^")`

```{r}
#| results: asis
aut$get_affiliations() |> cat(sep = "\n\n")
```


<!-- # Contents -->
\tableofcontents
\newpage
\setcounter{section}{0}
\setcounter{page}{0}
\pagenumbering{arabic}

# Introduction

We write smart things and we cite stuff [@corriher2008bakewise].

Inline @lee2012literature blablabla.

Or just the year -@barham2001science and nothing else.

We can also cite a paper where we are co author [@delatourte2025] and the name will not be in bold in the references list.

# Aims of this thesis

\lipsum

## Sub section


\lipsum


# References {.unnumbered}

::: {#refs}
:::
